E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-13 Background/history.tex
slight formatting changes done
fixed most emph/quote/texttt issues

\section{History of E-Mail Injection}

E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \dq{\texttt{mail}} function in PHP, and how it can be exploited. More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.

As this vulnerability was initially found in the \emph{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \emph{mail()} implementation of PHP 4.0.

The vulnerability was also described briefly (less than a page) by Stuttard and Pinto in their widely acclaimed book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. 
A concise timeline of the vulnerability is presented in Table~\ref{tab:history}.

An example of the vulnerable code written in PHP is shown in Listing~\ref{code:phpemi}. This code takes in user input from the PHP superglobal \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, and stores it in the variable \dq{\texttt{\$from}}, which is later passed to the \dq{\texttt{mail}} function to construct and send the e-mail.
\input{Background/php.tex}

When this code is given the malicious input \dq{\texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}}} as the value of the \dq{\texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the `CC' (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the `CC' as well.
\input{Background/smtpheaders}
\input{Background/history_table}

>>>>

\subsection{History of E-Mail Injection}

E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited. More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.

As this vulnerability was initially found in the \texttt{mail()} function of PHP, E-Mail Header Injection can be traced to as early as the beginning of the 2000's, present in the \texttt{mail()} implementation of PHP 4.0.

An example of the vulnerable code written in PHP is shown in Listing~\ref{code:phpemi}. This code takes in user input from the PHP superglobal \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, and stores it in the variable \texttt{\$from}, which is later passed to the \texttt{mail()} function to construct and send the e-mail.
\input{Background/php.tex}

When this code is given the malicious input \texttt{\lstinline{sai@sai.com\\nBCC:spc@spc.com}} as the value of the \texttt{\$\_REQUEST[\textquotesingle email\textquotesingle]}, it generates the SMTP Headers shown in Listing~\ref{code:smtpheaders}. It can be seen that the \texttt{CC} (carbon copy) header that we injected appears as part of the resulting SMTP message. This will make the e-mail get sent to the e-mail address specified as part of the \texttt{CC} as well.
\input{Background/smtpheaders}
%\input{Background/history_table}

### 2016-05-13 Background/impact.tex
slight formatting changes done
fixed most emph/quote/texttt issues

\section{Potential Impact}

@@

	\item Spam Networks\\
	Spam networks can use E-Mail Header Injection vulnerabilities on the ability to send a large amount of e-mail from servers that are trusted. By adding additional \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers to the generated e-mail, attackers can easily achieve this effect.

@@

	\item Information Extraction of legitimate users\\
	E-Mails can contains sensitive data that is meant to be accessed only by the user. Due to E-Mail Header Injection, an attacker can easily add a \dq{\texttt{bcc}} header, and send the e-mail to himself, thereby extracting important information.
	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

>>>>

\subsection{Potential Impact}

@@

	\item Spam Networks\\
	Spam networks can use E-Mail Header Injection vulnerabilities on the ability to send a large amount of e-mail from servers that are trusted. By adding additional \texttt{cc} or \texttt{bcc} headers to the generated e-mail, attackers can easily achieve this effect.

@@

	\item Information Extraction of legitimate users\\
	E-Mails can contains sensitive data that is meant to be accessed only by the user. Due to E-Mail Header Injection, an attacker can easily add a \texttt{bcc} header, and send the e-mail to himself, thereby extracting important information.
	User privacy can thus be compromised, and loss of private information can by itself lead to other attacks.

### 2016-05-13 Discussion/lessons.tex
chap6 added
fixed most emph/quote/texttt issues

\section{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats \cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

	We come to this conclusion because of our discovery of the \dq{\texttt{To header injection}}. Clearly, this is possible due to incomplete sanitization performed by the application. We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks. We would also like to remark that \dq{\texttt{To header injection}} is not complete E-Mail Header Injection, but only a special subset.

@@

    From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail. We identify this with the presence of both the \dq{\texttt{bcc}} header and the \dq{\texttt{x-check}} header. This is the most potent form of the vulnerability and is found on quite a few websites. This is also the vulnerability that is documented and discussed on many websites.

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \dq{\texttt{To}} field. We christened this as \dq{\texttt{To header injection}}. In this form of the vulnerability, we are able to simply add addresses to the \dq{\texttt{To}} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \dq{\texttt{To header injection}} was possible on 142 forms, while spoofing using \dq{\texttt{To header injection}} was possible on 11 forms.

>>>>

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats \cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

	We come to this conclusion because of our discovery of the \texttt{To header injection}. Clearly, this is possible due to incomplete sanitization performed by the application. We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks. We would also like to remark that \texttt{To header injection} is not complete E-Mail Header Injection, but only a special subset.

@@

    From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail. We identify this with the presence of both the \texttt{bcc} header and the \texttt{x-check} header. This is the most potent form of the vulnerability and is found on quite a few websites. This is also the vulnerability that is documented and discussed on many websites.

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field. We christened this as \texttt{To header injection}. In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 142 forms, while spoofing using \texttt{To header injection} was possible on 11 forms.

### 2016-05-13 Discussion/limits.tex
chap6 added
fixed most emph/quote/texttt issues

\section[Limitations]{Limitations of the Project}
\label{limitations}
	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
	\begin{itemize}
		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system. As CAPTCHAs are designed to be robust, there is no easy way to break them. There has been considerable research in this area \cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.

@@

		\item Blogs powered by WordPress/Drupal\\
        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress `plugins' also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms. Some of these plugins are discussed in the following section. Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on very few sites powered by WordPress.

@@

        \item Websites that are not in English\\
        Because we are only searching for the words `e-mail', `mail' or `email' within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for `e-mail' --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
	\end{itemize}

>>>>

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
	\begin{itemize}
		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system. As CAPTCHAs are designed to be robust, there is no easy way to break them. There has been considerable research in this area \cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.

@@

		\item Blogs powered by WordPress/Drupal\\
        In addition to what was discussed in Section \ref{issues:cms}, we found that certain WordPress plugins also prevent the E-Mail Header Injection attack by sanitizing user input on Contact Forms. Some of these plugins are discussed in the following section. Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on very few sites powered by WordPress.

@@

        \item Websites that are not in English\\
        Because we are only searching for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail} --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.
	\end{itemize}

### 2016-05-13 Results/analysis.tex
fixed most emph/quote/texttt issues

\subsection[Analysis of Data]{Our Analysis of the received e-mail Data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \dq{\texttt{bcc}} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

	\item E-Mails with the \dq{\texttt{to}} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen `TO~header injection'. These injections reflect the ability to inject any number of e-mail addresses into the \dq{\texttt{to}} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, `TO header injection' makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

	\item E-Mails with the \dq{\texttt{x-check}} header successfully injected\\
    The third category of e-mails received were e-mails with the \dq{\texttt{x-check}} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \dq{\texttt{bcc}} header can be injected into the generated e-mail. 
\end{enumerate}
We list each category and the number of e-mails received by the category in Table~\ref{tab:analysis}.

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \dq{\texttt{bcc}} and \dq{\texttt{x-check}} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 75\% of the received \dq{\texttt{bcc}} header injected e-mails are also susceptible to other header injections.

	\item Both \dq{\texttt{To}} header injections and \dq{\texttt{x-check}} headers \\
	This combination shows us that in addition to being able to inject into the \dq{\texttt{To}} fields, we are able to inject additional headers into the e-mail. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.

	\item \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
	In addition to analyzing the `maluser' account, we also analyze emails received by the `nuser' account. We explain the presence of these headers in the following paragraph.

	\item Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\\
	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the `maluser' account. We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.

	\item Total successful injections\\
	This represents the total number of successful injections our system made. This includes the E-Mail Header Injections with \dq{\texttt{bcc}} header\,(1), \dq{\texttt{To}} header injections alone\,(3), and Unique \dq{\texttt{x-check}} headers found in `nuser' e-mails\,(7). This is the total number of vulnerabilities that were found by our system.

>>>>

\subsection[Analysis of Data]{Our Analysis of the received e-mail Data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \texttt{bcc} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

	\item E-Mails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen \texttt{TO~header injection}. These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, \texttt{TO header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

	\item E-Mails with the \texttt{x-check} header successfully injected\\
    The third category of e-mails received were e-mails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \texttt{bcc} header can be injected into the generated e-mail. 
\end{enumerate}
We list each category and the number of e-mails received by the category in Table~\ref{tab:analysis}.

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 75\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.

	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we are able to inject additional headers into the e-mail. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.

	\item \texttt{x-check} headers found in \texttt{nuser} e-mails\\
	In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account. We explain the presence of these headers in the following paragraph.

	\item Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\\
	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the \texttt{maluser} account. We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.

	\item Total successful injections\\
	This represents the total number of successful injections our system made. This includes the E-Mail Header Injections with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\,(7). This is the total number of vulnerabilities that were found by our system.

### 2016-05-13 Results/data_analysis.tex
fixed most emph/quote/texttt issues

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with `bcc' header & 265\\
		\hline
		2 & E-Mail Header Injections with `x-check' header & 214\\
		\hline
		3 & `To header' injections alone & 142\\
		\hline
		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
		\hline
		5 & Both `To header' injections and x-check headers &
		11\\
		\hline
		6 & `x-check' headers found in `nuser' e-mails & 56\\
		\hline
		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
		\hline
		8 & Total successful injections (1 + 3 + 7) & 433\\

>>>>

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with \texttt{bcc} header & 265\\
		\hline
		2 & E-Mail Header Injections with \texttt{x-check} header & 214\\
		\hline
		3 & \texttt{To header} injections alone & 142\\
		\hline
		4 & E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 188\\
		\hline
		5 & Both \texttt{To header} injections and x-check headers &
		11\\
		\hline
		6 & \texttt{x-check} headers found in \texttt{nuser} e-mails & 56\\
		\hline
		7 & Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 26\\
		\hline
		8 & Total successful injections (1 + 3 + 7) & 433\\

### 2016-05-13 System/assumptions.tex
chap3 added
fixed most emph/quote/texttt issues

\section{Assumptions}
We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

@@

	\item \textbf{Injection of \dq{\texttt{bcc}} indicates the existence of E-Mail Header Injection Vulnerability} \\
	We assume that the ability to inject a \dq{\texttt{bcc}} header field is proof that the E-Mail Header Injection vulnerability exists in the application. We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.
	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting E-Mail Header Injection vulnerability.
\end{enumerate}

>>>>

\subsection{Assumptions}
We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

@@

	\item \textbf{Injection of \texttt{bcc} indicates the existence of E-Mail Header Injection Vulnerability} \\
	We assume that the ability to inject a \texttt{bcc} header field is proof that the E-Mail Header Injection vulnerability exists in the application. We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.
	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting E-Mail Header Injection vulnerability.
\end{enumerate}
